04_DESeq_sexes

### 2019-05-23 analysis/04_DESeq2_sexes.Rmd
done with pca for now

colorpenultimatebad <- c("control" = "#636363", 
                      "nestbldg" = "#fb6a4a", 
                      "incubate begin" = "#a1d99b",
                   "incubate middle" = "#74c476", 
                   "incubate end" = "#31a354",  
                   "eggs late" = "#006d2c",
                   "nestling begin" = "#cbc9e2",   
                   "nestling middle" = "#9e9ac8", 
                   "nestling end" = "#6a51a3")

@@

```{r pcadf}
p1 <- plotPCAs(dds.female_hypothalamus, "female hypothalamus")
p2 <- plotPCAs(dds.female_pituitary, "female pituitary")      
p3 <- plotPCAs(dds.female_gonad, "female gonad")
p4 <- plotPCAs(dds.male_hypothalamus, "male hypothalamus")
p5 <- plotPCAs(dds.male_pituitary, "male pituitary")
p6 <- plotPCAs(dds.male_gondad, "male gonad")
p1
p2
p3
p4
p5
p6
```

```{r pca, fig.dim = c(12, 10)}
mylegend <- get_legend(p1)

allPC1s <- plot_grid(p1 +  theme(legend.position = "none",
               axis.title.x=element_blank(),axis.text.x=element_blank(), axis.ticks.x=element_blank()), 
    p4 + theme(legend.position = "none",
               axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank()), 
    p2 + theme(legend.position = "none",
               axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank()),
    p5 + theme(legend.position = "none",
               axis.title.x=element_blank(), axis.text.x=element_blank(),axis.ticks.x=element_blank()),
    p3 + theme(legend.position = "none", axis.ticks.x=element_blank()),
    p6 + theme(legend.position = "none", axis.ticks.x=element_blank()),
    nrow = 3, rel_heights = c(0.3, 0.3, 0.4))

pc1grid <- plot_grid(allPC1s, mylegend, ncol = 2, rel_widths = c(1.0, 0.15))
pc1grid

pdf("../figures/sexes/pc1grid.pdf", width = 12, height = 10)
plot(pc1grid)
dev.off()

@@

>>>>

colorpenultimatebad <- c("control" = "#636363", 
                      "nestbldg" = "#fb6a4a", 
                      "incubate begin" = "#a1d99b",
                   "incubate middle" = "#74c476", 
                   "incubate end" = "#31a354",  
                   "eggs late" = "#006d2c",
                   "nestling begin" = "#9e9ac8",   
                   "nestling middle" = "#6a51a3", 
                   "nestling end" = "#3f007d")

@@

```{r pcadf}
p1 <- plotPCAs(dds.female_hypothalamus, "female hypothalamus")
p2 <- plotPCAs(dds.female_pituitary, "female pituitary")      
p3 <- plotPCAs(dds.female_gonad, "female gonad")
p4 <- plotPCAs(dds.male_hypothalamus, "male hypothalamus")
p5 <- plotPCAs(dds.male_pituitary, "male pituitary")
p6 <- plotPCAs(dds.male_gondad, "male gonad")
p1
p2
p3
p4
p5
p6

@@

```{r pca, fig.dim = c(12, 10), eval=T}
mylegend <- get_legend(p1)

theme_noaxislabels <- theme(legend.position = "none", axis.title.x=element_blank(),axis.text.x=element_blank())

allPC1s <- plot_grid(p1 + theme_noaxislabels, 
                     p1 + theme_noaxislabels, 
                     p1 + theme_noaxislabels,
                     p1 + theme_noaxislabels,
                     p1 + theme(legend.position = "none"),
                     p1 + theme(legend.position = "none"),
                     nrow = 3, rel_heights = c(0.3, 0.3, 0.4))

pc1 <- plot_grid(mylegend, allPC1s, nrow = 2, rel_heights = c(0.15, 1.0))
pc1

pdf("../figures/sexes/pca-1.pdf", width = 12, height = 10)
plot(pc1)
dev.off()
```
